---
title: "What the package does"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{What the package does}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753davi0682)
```

# Introduction
This package is about the applications to data using R. 

## Reading in data
To read in csv files into R work space, we can use `read.csv()`.
```{r, eval=FALSE}
data
```

## Vector creation
We can create a vector by using the `c()` function. 
```{r}
v <- c(1,4,5)
v
```

## Creation of lists
To create a list, we can use the function `list`.
```{r}
l <- list(a = 1:20, b = letters, c = rnorm(10))
l
```

## Creation of a matrix of NA's
```{r}
mat <- matrix(NA, 
              nrow= 10,
              ncol = 5,
              byrow = TRUE
              )
mat
```

## Creating data frames
To create a data frame, we can use `data.frame()`
```{r}
df <- data.frame(a=1:26, b = letters, c = LETTERS, d= rnorm(26))
head(df)
```


# Functions
This package includes 9 functions from the labs.

## myscatterhist function
This function outputs scatter histogram of two vectors.
```{r}
with(ddt, scatterhist(LENGTH,WEIGHT, xlab="LENGTH"))
```

## mysample function
This function outputs a bar plot showing the relative frequency of the numbers (10) from n times of random drawing. 
```{r}
mysample(n=1000,iter=1,time=1)
```

## myncurve function
This functions output the plot of normal distribution, and the probability P=(Y <= x).
```{r}
myncurve(mu=10,sigma=5,x=6)
```

## mybinomial function
This function outputs a bar plot of the relative frequency of the times of the success in a binomial test.
```{r}
mybin(10000,10,.7)
```

